The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-14 talk/vmil2012/paper.tex
We are using a specific revision and not a tag anymore

The results presented in this section are based on numbers gathered by running
a subset of the standard PyPy benchmarks. The PyPy benchmarks are used to
measure the performance of PyPy and are composed of a series of
micro-benchmarks and larger programs.\footnote{\url{http://speed.pypy.org/}} The
benchmarks were taken from the PyPy benchmarks repository using revision
\texttt{ff7b35837d0f}.\footnote{\url{https://bitbucket.org/pypy/benchmarks/src/ff7b35837d0f}}
The benchmarks were run on a version of PyPy based on the
tag~\texttt{0b77afaafdd0} and patched to collect additional data about the
guards in the machine code
backends.\footnote{\url{https://bitbucket.org/pypy/pypy/src/0b77afaafdd0}} The
tools used to run and evaluate the benchmarks including the patches applied to
the PyPy sourcecode can be found in the repository for this
paper.\footnote{\url{https://bitbucket.org/pypy/extradoc/src/tip/talk/vmil2012}}
All
benchmark data was collected on a MacBook Pro 64 bit running Max OS 10.8 with
the loop unrolling optimization disabled.\footnote{Since loop unrolling
duplicates the body of loops it would no longer be possible to meaningfully
compare the number of operations before and after optimization. Loop unrolling
is most effective for numeric kernels, so the benchmarks presented here are not
affected much by its absence.}

>>>>

The results presented in this section are based on numbers gathered by running
a subset of the standard PyPy benchmarks. The PyPy benchmarks are used to
measure the performance of PyPy and are composed of a series of
micro-benchmarks and larger programs.\footnote{\url{http://speed.pypy.org/}} The
benchmarks were taken from the PyPy benchmarks repository using revision
\texttt{ff7b35837d0f}.\footnote{\url{https://bitbucket.org/pypy/benchmarks/src/ff7b35837d0f}}
The benchmarks were run on a version of PyPy based on the
revision~\texttt{0b77afaafdd0} and patched to collect additional data about the
guards in the machine code
backends.\footnote{\url{https://bitbucket.org/pypy/pypy/src/0b77afaafdd0}} The
tools used to run and evaluate the benchmarks including the patches applied to
the PyPy sourcecode can be found in the repository for this
paper.\footnote{\url{https://bitbucket.org/pypy/extradoc/src/tip/talk/vmil2012}}
All
benchmark data was collected on a MacBook Pro 64 bit running Max OS 10.8 with
the loop unrolling optimization disabled.\footnote{Since loop unrolling
duplicates the body of loops it would no longer be possible to meaningfully
compare the number of operations before and after optimization. Loop unrolling
is most effective for numeric kernels, so the benchmarks presented here are not
affected much by its absence.}
